Factorization Algebras and Factorization Homology on Stratified Spaces

### 2024-03-27 text_condensed.tex
First pass of a condensed version. Fell free to change at will.

\documentclass[../text]{subfiles}

@@

@@

Factorization algebras are a rigorous way to capture the idea of assigning an object to each piece of a space, together with a local-to-global principle that allows one to find out about larger pieces from smaller ones. The first ideas around factorization algebras were introduced by \cite{bd2004} in the context of vertex algebras in CFTs. These were geometric in nature. The topological version that we present was then introduced by Lurie and subsequently further developed in \cite{cg2016}, especially for the purposes of mathematical physics. Here we will present these ideas following \cite{cg2016} and also \cite{af_primer}. A similar exposition can be found in \cite{ginot2015}.

\begin{remark}
    We note that we have fixed a symmetric monoidal $\infty$-category $\catC$ that is $\otimes$-presentable to serve as the $\infty$-category that our algebras will be valued in.
\end{remark}

@@

\begin{remark}
    It is obvious that in the case of (stratified) manifolds we have already seen alternative notation for the $\infty$-operad $\opens(X)$ before, namely $\mfld[r]_{/M}$. This makes a connection to the standard notation used around factorization homology, and is something that we'll make use of later.
\end{remark}

@@

\begin{remark}
    The category $\opens[r](X)$ can be replaced with any other category that supports an analogue of the Weiss Grothendieck topology. In the case of (stratified) manifolds, $\opens[r](X)$ is already the same as $\mfld[r]_{/X}$, be we could just as well define Weiss cosheaves on $\mfld[r]$, i.e. $\csheaves[W](\mfld[r], \catC)$. If we're working with the $\infty$-categories $\mfld$ or $\mfld_{/X}$, then we define cosheaves on them through the pullback
    %
    \begin{equation}
        \begin{tikzcd}
            \csheaves[W] (\mfld, \catC) \arrow[dr, phantom, "\ulcorner", very near start] \arrow[r] \arrow[d] & \mathsf{Fun}(\mfld, \catC) \arrow[d] \\
            \csheaves[W] (\mfld[r], \catC) \arrow[r] & \mathsf{Fun}(\mfld[r], \catC),
        \end{tikzcd}
    \end{equation}
    %
    and similarly for the relative case $\mfld_{/X}$.
\end{remark}

@@

\begin{remark}\label{rem:check_nerve}
    A factorization algebra is a prefactorization algebra whose restriction to $\opens[r](X)$ is a Weiss cosheaf. This means that the definition can be rewritten in an equivalent way as with all cosheaves. Following \cite{nlab} (which presents the dual case of sheaves) we can express the condition through the \v{C}ech nerve. Let $\mathscr{U}_U = \{ U_i \rightarrow U\}_{i \in I}$ be a (Weiss) cover of an open set $U$ and $F$ be a copresheaf, and define the simplicial object
    %
    \begin{equation}
        \cech_{\bullet}(\mathscr{U}_U, F) := \left( \coprod_{i \in I} F(U_i) \leftleftarrows \coprod_{i, j \in I} F(U_i \cap U_j) \mathrel{\substack{\textstyle\leftarrow\\[-0.6ex]
        \textstyle\leftarrow\\[-0.6ex]\textstyle\leftarrow}} \coprod_{i, j, k \in I} F(U_i \cap U_j \cap U_k) \mathrel{\substack{\textstyle\leftarrow\\[-0.6ex]\textstyle\leftarrow\\[-0.6ex]\textstyle\leftarrow\\[-0.6ex]\textstyle\leftarrow}} \cdots  \right),
    \end{equation}
    %
    where the maps are induced by the value of $F$ on the inclusions of opens. There are canonical maps $F(U_i) \rightarrow F(U)$, so that at the level of simplicial objects there is a canonical map
    %
    \begin{equation}
        \cech_{\bullet} (\mathscr{U}_U, F) \xrightarrow{\quad} F(U)_{\bullet},
    \end{equation}
    %
    to the constant simplicial complex at $F(U)$. Since $\catC$ has (sifted) colimits we can take the geometric realization to obtain a morphism
    %
    \begin{equation}
        \cech(\mathscr{U}_U, F) \xrightarrow{\quad} F(U).
    \end{equation}
    %
    $F$ is a (homotopy) cosheaf if, and only if, this morphism is an equivalence for every open set $U$ and every Weiss cover of it $\mathscr{U}_U$.
\end{remark}

All of our definitions above are valid for all topological spaces, so in particular, also the stratified spaces we introduced at the beginning. For the next definition of locally constant factorization algebras though, it will be important to specify more information about the space. In other words, they will capture information about the stratification.

There is a general definition of locally constant algebra objects in the context of any $\infty$-operad given in \cite[def.2.3.3.20]{lurie_ha}, which, of course, applies here. In our case one can also take a perspective more akin to \cite[def.A.1.12]{lurie_ha} by defining locally constant cosheaves and then pulling back this property to factorization algebras. This is what we will do, along with focusing our attention to stratified (and therefore also to smooth) manifolds. The definitions we will make can in a lot of cases also be expanded for any $C^0$ stratified space or topological manifold.

@@

\begin{definition}
    The $\infty$-category $\lcfa_M (\catC)$ of \emph{locally constant factorization algebras on a stratified manifold $M$ valued in $\catC$} is the full $\infty$-subcategory of $\falg_M (\catC)$ as in the pullback
    %
    \begin{equation}
        \begin{tikzcd}
            \lcfa_M (\catC) \arrow[dr, phantom, "\ulcorner", very near start] \arrow[r] \arrow[d] & \falg_M (\catC) \arrow[d] \\
            \csheaves[W, lc]_M (\catC) \arrow[r] & \csheaves[W]_M (\catC).
        \end{tikzcd}
    \end{equation}
\end{definition}

\begin{remark}\label{rem:sym_mon_inheritance}
    The $\infty$-categories of factorization algebras of all varieties acquire a symmetric monoidal structure from the symmetric monoidal structure of $\catC$ pointwise
    %
    \begin{equation}
        (F \otimes G)(U) = F(U) \otimes G(U).
    \end{equation}
    %
    The only subtlety is the cosheaf condition, where the symmetric monoidal structure is induced only if we also take into account that in $\catC$ colimits commute with its symmetric monoidal structure.

@@

\begin{remark}
    One perspective on this result, provided by \cite[...]{aft_fhstrat}, is that the theory of locally constant factorization algebras captures as much information as (generalized) homology theory in the sense of \cite[...]{aft_fhstrat}.
\end{remark}

@@

>>>>

% Run only with XeLaTeX!
%---------------------------------------------------------------------
%	FORMATING AND TYPESETTING
%---------------------------------------------------------------------

% Set document class
\documentclass[12pt,a4paper]{article}

% Option to change margin size
\usepackage[margin=2cm]{geometry}

% Font and encoding settings
\usepackage[T1]{fontenc}
%\usepackage[utf8]{inputenc} not necessary with xelatex?
\usepackage{yfonts} % germanic fonts (fraktur...)
%\defaultfontfeatures{Ligatures=TeX} %??

% Footnotes
\usepackage[stable]{footmisc}

% Indentation and spacing
\usepackage{indentfirst} % indentation
\usepackage{enumitem}[leftmargin=0pt] % spacing
\setlist{nosep}

% Multi column environment
\usepackage{multicol}

% Formating of titles
\usepackage{titlesec}
\titleformat{\section}
{\normalfont\large\bfseries}{\thesection}{1em}{}
\titleformat{\subsection}
{\normalfont\normalsize\bfseries}{\thesubsection}{1em}{}
\titleformat{\subsubsection}
{\normalfont\small\bfseries}{\thesubsubsection}{1em}{}
\titleformat{\paragraph}[runin]
{\normalfont\small\bfseries}{\theparagraph}{1em}{}
\titleformat{\subparagraph}[runin]
{\normalfont\small\bfseries}{\thesubparagraph}{1em}{}
\usepackage[titletoc]{appendix}

% Math typesetting packages
\usepackage{amsmath, amssymb, amsthm, mathtools, commath}
\usepackage[warnings-off={mathtools-colon,mathtools-overbracket}]{unicode-math} % makes \mathbb{1} work and changes font of mathbb
\usepackage[mathscr]{euscript} % euler script font
\usepackage{tikz-cd} % tikz commutative diagrams
\usepackage{thmtools, thm-restate} % theorem tools, especially restatable

\AtBeginDocument{\renewcommand\setminus{\smallsetminus}} % \setminus doesn't work in unicode-math

%---------------------------------------------------------------------

%---------------------------------------------------------------------
%	GRAPHICS
%---------------------------------------------------------------------

\usepackage{float}
\usepackage{caption}
\usepackage{graphicx}
\graphicspath{{images/}}

\usepackage{pdfpages} % for inserting pdf pages

%---------------------------------------------------------------------

%---------------------------------------------------------------------
%	BIBLIOGRAPHY
%---------------------------------------------------------------------

\usepackage[backend=biber,style=alphabetic]{biblatex}
\renewcommand*{\bibfont}{\small}
\addbibresource{text.bib}

%---------------------------------------------------------------------

%---------------------------------------------------------------------
%	HYPERLINKS
%---------------------------------------------------------------------

% Define the colors
\usepackage{xcolor}
\definecolor{brown}{HTML}{CD853F}
\definecolor{blue}{HTML}{4169E1}
\definecolor{green}{HTML}{2E8B57}

% Setup options for hyperlinks
\usepackage{hyperref}
\hypersetup{
colorlinks=true, linkcolor=black, breaklinks=true,
linktoc=all, bookmarksnumbered=true,
urlcolor=brown, linkcolor=blue, citecolor=green, % Link colors
}

% Referencing package
\usepackage{cleveref}
\crefname{section}{\S\!}{\S\S\!}
\Crefname{section}{\S\!}{\S\S\!}

%---------------------------------------------------------------------
%	THEOREM STYLES
%---------------------------------------------------------------------

% Define a dummy counter to keep count for all sub-environments
\newcounter{counter} \numberwithin{counter}{section}

% Define theorem styles here based on the definition style
\theoremstyle{definition}
\newtheorem{definition}[counter]{Definition}
\newtheorem{construction}[counter]{Construction}
\newtheorem{observation}[counter]{Observation}

% Define theorem styles here based on the plain style
\theoremstyle{plain} 
\newtheorem{theorem}[counter]{Theorem}
\newtheorem*{theorem*}{Theorem}
\newtheorem{corollary}[counter]{Corollary}
\newtheorem{lemma}[counter]{Lemma}
\newtheorem{proposition}[counter]{Proposition}
\newtheorem*{proposition*}{Proposition}
\newtheorem{conjecture}[counter]{Conjecture}

% Define theorem styles here based on the remark style
\theoremstyle{remark}
\newtheorem{example}[counter]{Example}
\newtheorem{remark}[counter]{Remark}

%---------------------------------------------------------------------

%---------------------------------------------------------------------
%	NEW COMMANDS
%---------------------------------------------------------------------

% general target category
\newcommand{\catC}{\mathscr{C}}

% categories of factorization algebras
\newcommand{\falg}{\mathscr{F} \mathsf{Alg}}
\newcommand{\lcfa}{\mathscr{F} \mathsf{Alg}^{\mathsf{lc}}}

% category of manifolds
\newcommand{\mfld}[1][s]{%
    \ifx r#1\mathsf{Mfld}\else
    \ifx s#1\mathscr{M} \mathsf{fld}\else
    \mathrm{Illegal~option}%
    \fi\fi
}

% category of disks
\newcommand{\disk}[1][s]{%
    \ifx r#1\mathsf{Disk}\else
    \ifx s#1\mathscr{D} \mathsf{isk}\else
    \mathrm{Illegal~option}%
    \fi\fi
}

% category of opens
\newcommand{\opens}[1][s]{%
    \ifx r#1\mathsf{Opns}\else
    \ifx s#1\mathscr{O} \mathsf{pns}\else
    \mathrm{Illegal~option}%
    \fi\fi
}

% category of cosheaves
\newcommand{\csheaves}[1][n]{%
    \ifx n#1 \mathsf{c} \mathscr{S} \mathsf{hv}\else
    \mathsf{c} \mathscr{S} \mathsf{hv}^{\mathsf{#1}}
    \fi
}

% category of infinity categories
\newcommand{\cat}{\mathscr{C} \mathsf{at}_{\infty}}

% template for category of algebras
\newcommand{\alg}[1]{\mathscr{A} \mathsf{lg}_{#1}}

% template for category of locally constant algebras
\newcommand{\lcalg}[1]{\mathscr{A} \mathsf{lg}^{\mathsf{lc}}_{#1}}

% half-open interval
\newcommand{\hoint}{\mathbb{R}_{\geq 0}}

% Cech complex
\newcommand{\cech}{\check{\mathsf{C}}}

% Category of basics
\newcommand{\bsc}{\mathscr{B} \mathsf{sc}}
\newcommand{\bstr}{\mathscr{B}}

% Open cone
\newcommand{\cone}[1][n]{%
    \ifx b#1\overline{\mathsf{C}}\else
    \ifx n#1\mathsf{C}\else
    \mathrm{Illegal~option}%
    \fi\fi
}

%---------------------------------------------------------------------

%\usepackage{subfiles}

\setcounter{section}{-1}

@@

% Set title, author and date
\title{Factorization Algebras and Factorization Homology on Stratified Spaces}
\author{Aleksandar Ivanov, Ödül Tetik}
\date{}
\maketitle

\begin{abstract}
    We endeavor to fully describe (locally constant) factorization algebras on stratified spaces, by giving a description of the $\infty$-operad that underlies them through the use of factorization homology. We also give a result about a collar-gluing property that the $\infty$-categories of (locally constant) factorization algebras satisfy, which enables novel descriptions of these on more complicated spaces. Finally, we outline a classification scheme for locally constant factorization algebras on some stratified manifolds. Parts of this work were adapted from a Master's thesis dissertation submitted to ETH Z\"urich for the first author.
\end{abstract}

\tableofcontents

\section{Introduction}

{\color{red} Needs to be rewritten slightly when we finalize decision on what to include.}

In this work we will explore the concepts of factorization algebras and factorization homology over stratified spaces. These two concepts, which at first sight will looks very different, will turn out to be closely related. We will strive to keep the discussion at the level of stratified spaces, while making a comparison to results in the smooth case. Some results we will meet have been proven in the smooth case, but with methods which do not (at the present moment) generalize to the stratified case. We will endeavor to point these out and give proofs that hold more generally. The outline of the text is as follows:

%\textbf{\Cref{ch:strat_spaces} Stratified Spaces:} The first section deals with setting up the theory of stratified spaces that we will use. It is essentially a recap of the necessary results from the work of Ayala, Francis and Tanaka (AFT) \cite{aft_localstrut}, which is one of our main sources. The idea and fundamentals of stratified spaces have existed for a long time in different incarnation beginning with the work of Whitney \cite{whitney92}. The reason why we choose to work with this particular version of stratified spaces is due to them supporting a notion of conical smoothness that is a generalization of smoothness of manifolds. Furthermore, the theory of factorization homology has been developed with these spaces in mind, which eases the process of extending certain results to the stratified case much easier. We will not go into the full details that this incarnation of the theory has to offer, but instead we will only mention results that we will make use of later on. Beyond conical smoothness, this will include tangential structure and its stratified generalization, together with the packaging of both of these data into the concept of an $\infty$-category of basic singularity types. For the proofs of these statements the reader is encouraged to consult \cite{aft_localstrut}.

%\textbf{\Cref{ch:fact_hom} Factorization Homology:} The second section will present the theory of factorization homology. Similar to the first section this will mostly be a recap of useful results developed by Ayala, Francis and Tanaka. Specifically, the stratified space results can be found in \cite{aft_fhstrat}, while the results for topological manifolds can be found in \cite{af_fhtop}. For the purposes of the theory we will need the concept of (structured) disk algebras, since this will be the algebraic input. Factorization homology will then combine this with the data of a specific kind of (possibly stratified) manifold into an object that can be viewed either as an invariant of the manifold or an invariant of the algebra. We will explore the key example of factorization homology over the closed, oriented interval $[-1,1]$, and see how this gives rise to the algebraic concept of the two-sided bar construction. More generally, this underpins the theory because it codifies the property of $\otimes$-excision. Finally, we will also state a classification result \cite[prop.4.8]{aft_fhstrat} about a certain type of disk algebras with stratified structure.

\textbf{\Cref{ch:fact_alg} Factorization Algebras:} The third section introduces the concept of factorization algebras, together with its different variations, like prefactorization algebras and locally constant factorization algebras. Of these, the locally constant factorization algebras will be the ones that capture the different possible stratified structures that a manifold can have, and they will be a large focus of this work. The definitions of these will not be novel. They can be found in the works \cite{cg2016}, \cite{ginot2015} and even \cite{af_primer}. In fact, in the slightly different context of vertex algebras the idea can be traced back to \cite{bd2004}. However, all of the above works take a slightly different perspective in their presentation of the definitions, which we hope to unite in this work. The key result of this section is the following:
%
\begin{theorem*}[\ref{thm:disk_alg=lcfa}]
    There is an equivalence of $\infty$-categories between locally constant factorization algebras over a stratified manifold $M$ and $\disk_{/M}$-algebras
    %
    \begin{equation}
        \int: \alg{\disk_{/M}} (\catC) \xrightarrow{\ \ \simeq \ \ } \lcfa_M (\catC),
    \end{equation}
    %
    given by factorization homology,
\end{theorem*}
%
as well as its \Cref{cor:disk_alg=falg} for the case of ordinary factorization algebras. These show that the $\infty$-operad governing factorization algebras can be taken to be the slice $\infty$-operad $\disk_{/M}$ (or $\disk[r]_{/M}$ for the ordinary case). We then introduce some operations that we can do with factorization algebras like the pushforward and restriction, as well as state a result for locally constant factorization algebras on product spaces, which confirms a conjecture of \cite{ginot2015}:
%
\begin{proposition*}[\ref{prop:exp_of_products_lc}]
    Let $M$ and $N$ be stratified manifolds. There is an equivalence of $\infty$-categories
    %
    \begin{equation}
        \bar{\pi}: \lcfa_{M \times N}(\catC) \xrightarrow{\ \ \simeq \ \ } \lcfa_{M}(\lcfa_{N}(\catC)).
    \end{equation}
\end{proposition*}
%
Finally, we will examine some examples of factorization algebras whose construction is known, specifically, locally constant factorization algebras on the intervals $(-1,1)$, $[-1,1)$ and $[-1,1]$ as well as Euclidean spaces $\mathbb{R}^n$ more generally.

\textbf{\Cref{ch:gluing_disk_alg} Collar-gluings and Disk Algebras:} The fourth section presents a novel result about the behavior of certain types of factorization algebras under the operation of collar-gluing in the manifold variable. It essentially shows that we can reproduce factorization algebras on a stratified manifold if we know them on some particular pieces of it together with the data of how to glue them. Formally, we have
%
\begin{theorem*}[\ref{thm:gluing_lcfas}]
    Given a collar-gluing of stratified manifolds $f: M \rightarrow [-1,1]$, the $\infty$-category of locally constant factorization algebras is equivalent to the pullback of $\infty$-categories
    %
    \begin{equation}
        \lcfa_{M} (\catC) \simeq \lcfa_{M_-} (\catC) \bigtimes_{\lcfa{M_0 \times \mathbb{R}} (\catC)} \\cfa_{M_+} (\catC).
    \end{equation}
\end{theorem*}
%
The results of the previous section a very important in the proof of this statement, because we heavily use the properties of factorization homology. A similar version holds for ordinary factorization algebras in the for of \Cref{cor:disk_alg=falg}. This result hugely expands the number of manifolds for which the $\infty$-category of locally constant factorization algebras can be specified. As a straightforward example, it gives a way to work on, and classify, factorization algebras on all higher spheres $S^n$. Without it, only the circle has been described to date (\cite{ginot2015}) using equivariant factorization algebras and inheritance from covering spaces.

\textbf{\Cref{ch:classif_defect_mfld} Classifying $\lcfa$s on Defect Manifolds:} The fifth section focuses on the stratified structure and gives a way to express what effect this has on the locally constant factorization algebras. Specifically, we look at the data of a smooth manifold $M$ with a distinguished, properly embedded submanifold $\Sigma$ (also known as a defect submanifold) as the data of a stratified manifold $M_\Sigma$. We will show that, along with giving algebras associated to the different pieces, locally constant factorization algebras on these manifolds, in some (precise) sense, also encode a module structure associated with $\Sigma$.

\textbf{Further Questions:} The exploration below naturally leads to questions that are beyond the scope of this work. As we will see, factorization algebras only need a topological space to be defined, but locally constant factorization algebras also capture information about the stratified structure. Neither of these, however, capture information about the tangential structure of the manifold, so the question arises:
%
\begin{itemize}
    \item Does there exist a version of factorization algebras that usefully capture information both about the stratified structure of a manifold and about its tangential structure?
\end{itemize}
%
The recent thesis \cite{pena2022} could provide a fruitful direction of exploration of the former concept. In a similar vein, \cite{cg2016} explain why it's important to have the concept of a $G$-equivariant factorization algebra, where $G$ is a Lie group. In particular, according to them, this asks for some definition of a smooth action of $G$ on factorization algebras.
%
\begin{itemize}
    \item Is there a suitable way to encompass this notion in the formalism presented here?
\end{itemize}
%
The beginnings of examining this idea can already be found in the thesis \cite{murray2020}, however the development there, while important, is still preliminary.

\subsection{Conventions on \texorpdfstring{$\infty$}{infinity}-categories}

The $\infty$-categories in this work will use the quasi-category model of $\infty$-category theory introduced by Joyal in \cite{joyal}, which is based on the simplicial sets introduced by \cite{bv73}. The work by Lurie in \cite{lurie_htt} and \cite{lurie_ha} greatly builds on this theory, and questions about fundamental objects or constructions that are in this text will always be answered in those references. This choice is because a great deal of the theory of factorization homology, as well as factorization algebras deal with $\infty$-categories of functors, which are most easily defined for quasi-categories.

It is also important to note that we will not be making a notational distinction between topological categories, Kan enriched categories and $\infty$-categories because of the functors
%
\begin{equation}
    \{ \mathsf{Top}\mathrm{-categories}\} \xrightarrow{\mathsf{Sing}} \{ \mathsf{Kan}\mathrm{-categories}\} \xrightarrow{\mathsf{N}} \cat,
\end{equation}
%
which are both Quillen--equivalences in appropriate ways (\cite{joyal2007quasi,bergner2010survey}). In particular, we will not distinguish notationally the nerve of an ordinary category from the ordinary category itself. Similarly, we will not distinguish between (topological) multicategories and their $\infty$-operadic nerve.

\subsection{Stratified Spaces}\label{ssec:strat_spaces}

The spaces that this work will be set in will very often be stratified spaces. Thus, we first need to define what we mean by this concept. There are multiple definitions of stratified spaces in the literature, all of which have their advantages and disadvantages. For our purposes, we will follow the account of \cite{aft_localstrut}. A compatible source is also \cite[sec.A.5]{lurie_ha}. The majority of the work on factorization homology has so far been elaborated using this particular set of definitions, and similarly the stratified spaces used in the literature on factorization algebras are usually subsumed too. Further details are, of course, discussed in the original \cite{aft_localstrut}, where one can find great explanations of the definitions that are needed, and detailed proofs of the theorems that can be proven.

\subsection{Factorization Homology}\label{ssec:fact_hom}

Factorization homology (also known as topological chiral homology) is a construction that to the data of a smooth manifold $M$ and an algebra $A$ valued in a symmetric monoidal $\infty$-category $\catC$ assigns an object
%
\begin{equation}
    \int_{M} A \in \catC.
\end{equation}
%
The physical interpretation is that given a spacetime $M$ and local observables $A$, $\int_MA$ returns global observables, though typically not all of them.

This implementation, with $M$ relaxed to a stratified manifold and $A$ to an appropriate type of algebra, is sometimes termed `alpha' factorization homology, as opposed to the `beta' version of \cite{ayala2020factorization} that evaluates $(\infty,n)$-categories on variframed stratified $n$-manifolds. In this work, we will be concerned, in this sense, with alpha factorization homology.

Fixing the algebra, the construction is functorial with respect to open embeddings in the manifold variable, which is the starting point to show that it is a chain level homology theory in a generalized sense. The initial chiral version was first introduced in \cite{bd2004}, and a topological version was introduced by \cite{lurie_ha}. The theory of factorization homology in the manner that we will recall here has been developed in \cite{francis2013,af_fhtop, aft_fhstrat}. We will also follow the introductory text \cite{af_primer}.

In the entirety of this work, we fix our target $\catC$ to be a symmetric monoidal $\infty$-category that is \emph{$\otimes$-presentable} \cite{af_fhtop}, i.e. it satisfies:
%
\begin{enumerate}
    \item $\catC$ is presentable: it admits colimits, and every object is a filtered colimit of compact objects, and
    \item the monoidal structure distributes over colimits: for all $c \in \catC$, the functor $c \otimes -: \catC \xrightarrow{} \catC$ takes colimit diagrams to colimit diagrams.
\end{enumerate}

\begin{remark}\label{rem:inherit_sym_mon_struct}
    For developing the theory of factorization homology the assumption that $\catC$ has all \emph{sifted} colimits, and that the monoidal structure commutes with these, is enough. However, if we want the $\infty$-category of algebras valued in $\catC$ to inherit the properties of having sifted colimits that commute with the monoidal structure, then we must require that $\catC$ has \emph{all} (small) colimits. This will similarly be the case for factorization algebras. The stronger requirement also doesn't exclude any of the core examples that we are interested in.
\end{remark}

\begin{example}
    The following are examples of $\otimes$-presentable categories:
    %
    \begin{enumerate}
        \item chain complexes $\mathscr{C}\mathsf{h}_{\mathbb{k}}$ over a commutative ring $\mathbb{k}$, where equivalences are given by quasi-isomorphism. The symmetric monoidal structure can be both direct sum $\oplus$ or tensor product $\otimes$.
        \item Any cocomplete, Cartesian closed $\infty$-category together with categorical product. (for example $\mathsf{Spaces}$ or $\cat$).
    \end{enumerate}
    %
    In particular, $(\mathscr{C}\mathsf{h}_{\mathbb{k}}, \otimes)$ is the most relevant for physical examples which is why it is the target of choice in \cite{cg2016} and \cite{ginot2015}.
\end{example}

We also fix an $\infty$-category of basics $\bstr \xrightarrow{} \bsc$.

\begin{remark}\label{rem:disk_b=disk_bsc}
    Since we will be dealing with the relative case for the majority of the work, and because $\disk(\bstr)_{/M}$ (and the related slice $\infty$-operads) does not actually depend on the particular tangential structure, as long as $M$ admits it, we will simplify our notation down to $\disk_{/M}$.
\end{remark}

\begin{remark}\label{rem:fin_equiv_natural}
    A few times in this work we will encounter the fact that a final functor $F: \mathscr{A} \xrightarrow{} \mathscr{B}$ between $\infty$-categories induces an equivalence
    %
    \begin{equation}\label{eq:fin_equivs_obj}
        \mathsf{colim}(G) \xrightarrow{\ \ \simeq \ \ } \mathsf{colim}(G \circ F),
    \end{equation}
    %
    for each functor $G: \mathscr{B} \xrightarrow{} \mathscr{C}$, whenever both colimits exist. We remark here that these equivalences are actually even natural in $G$. To explain this, we first notice that the equivalences in \Cref{eq:fin_equivs_obj} actually arise from equivalences between $\infty$-categories
    %
    \begin{equation}\label{eq:fin_equivs_cat}
        \mathscr{C}_{G/} \xrightarrow{\ \ \simeq \ \ } \mathscr{C}_{G \circ F /},
    \end{equation}
    %
    as discussed in \cite[prop.4.1.1.8]{lurie_htt}, where the functor is the obvious one. Furthermore, \cite[\href{https://kerodon.net/tag/016H}{016H}]{lurie_kerodon} tells us that the slice construction is functorial, which, after restricting, defines the functors
    %
    \begin{align}
        &S: \mathsf{Fun}(\mathscr{B}, \mathscr{C}) \xrightarrow{\ \ \ } \cat& \mathrm{and}& &S': \mathsf{Fun}(\mathscr{A}, \mathscr{C}) \xrightarrow{\ \ \ } \cat,&
    \end{align}
    %
    whose value on objects is given by $G \mapsto \mathscr{C}_{G/}$. We can now state that by naturality in $G$ we mean that the functors of \Cref{eq:fin_equivs_cat} assemble into an equivalence of functors   
    %
    \begin{equation}
        S \xrightarrow{\ \ \simeq \ \ } S' \circ F^*
    \end{equation}
    %
    in $\mathsf{Fun}(\mathsf{Fun(\mathscr{B}, \mathscr{C})}, \cat)$. But this is obviously the case, given the description of the maps in \Cref{eq:fin_equivs_cat}, and amounts to nothing more than bookkeeping.
\end{remark}

In particular, the above remark slightly extends \cite[prop.2.34]{aft_fhstrat}, as well as \cite[thm.2.25]{aft_fhstrat}, which become:
%
\begin{proposition}[{\cite[thm.2.34]{aft_fhstrat}}]\label{prop:barconst=intinterval}
    There is an equivalence of functors between the two-sided bar construction
    %
    \begin{equation}
        \mathsf{B}: \alg{\mathsf{Assoc^{RL}}}(\catC) \xrightarrow{} \catC
    \end{equation}
    %
    and factorization homology over the oriented closed interval
    %
    \begin{equation}
        \int_{[-1,1]}: \alg{\mathsf{Assoc^{RL}}}(\catC)\simeq \alg{\disk_{/[-1,1]}} (\catC) \xrightarrow{\ \int \ } \alg{\mfld_{/[-1,1]}} (\catC) \xrightarrow{\ \mathsf{ev}_{[-1,1]} \ } \catC.
    \end{equation}
    %
    In particular, given a unital, (homotopy) associative algebra $A$, a unital right $A$-module $R$ and a unital left $A$-module $L$, there is an equivalence of objects
    %
    \begin{equation}
        \int_{[-1,1]} (R, A, L) \xrightarrow{\ \ \simeq \ \ } R \bigotimes\limits_{A} L.
    \end{equation}
\end{proposition}

\begin{proposition}[{\cite[thm.2.25]{aft_fhstrat}}]\label{prop:fh_pushforward}
    Let $f: M \xrightarrow{} N$ be a weakly constructible bundle. There is a pushforward functor
    %
    \begin{equation}
        f_*: \alg{\disk_{/M}}(\catC) \xrightarrow{\quad} \alg{\disk_{/N}}(\catC).
    \end{equation}
    %
    This functor is such that there is a canonical equivalence between functors
    %
    \begin{equation}
        \int_M -, \int_N f_* - : \alg{\disk_{/M}} (\catC) \xrightarrow{\ \ \ \ } \catC.
    \end{equation}
\end{proposition}

@@

Factorization algebras are a rigorous way to capture the idea of assigning an object to each piece of a space, together with a local-to-global principle that allows one to find out about larger pieces from smaller ones. The first ideas around factorization algebras were introduced by \cite{bd2004} in the context of vertex algebras in CFTs. These were geometric in nature. The topological version that we present was then introduced by Lurie and subsequently further developed in \cite{cg2016}, especially for the purposes of mathematical physics.

Here we will present these ideas following \cite{cg2016} and \cite{ginot2015} while also trying to express them more categorically in the style of \cite{af_primer}. In this sense, the present work bridges a gap in how factorization algebras are usually presented.

@@

\begin{remark}
    Restricting to the case of (stratified) manifolds we have an alternative notation for the $\infty$-operad $\opens(X)$, namely $\mfld[r]_{/M}$. This makes a connection to the standard notation used around factorization homology, and is something that we'll make use of later.
\end{remark}

@@

\begin{remark}
    If we're working with the $\infty$-category $\mfld_{/X}$, then we define cosheaves on it through the pullback
    %
    \begin{equation}
        \begin{tikzcd}
            \csheaves[W] (\mfld_{/X}, \catC) \arrow[dr, phantom, "\ulcorner", very near start] \arrow[r] \arrow[d] & \mathsf{Fun}(\mfld_{/X}, \catC) \arrow[d] \\
            \csheaves[W] (\mfld_{/X}, \catC) \arrow[r] & \mathsf{Fun}(\mfld_{/X}, \catC).
        \end{tikzcd}
    \end{equation}
\end{remark}

@@

\begin{remark}\label{rem:cech_nerve}
    A factorization algebra is a prefactorization algebra whose restriction to $\opens[r](X)$ is a Weiss cosheaf. This means that the definition can be rewritten in an equivalent way as with all cosheaves. Following \cite{nlab} (which presents the dual case of sheaves) we can express the condition through the \v{C}ech nerve. Let $\mathscr{U}_U = \{ U_i \rightarrow U\}_{i \in I}$ be a (Weiss) cover of an open set $U$ and $F$ be a copresheaf, and define the simplicial object
    %
    \begin{equation}
        \cech_{\bullet}(\mathscr{U}_U, F) := \left( \coprod_{i \in I} F(U_i) \leftleftarrows \coprod_{i, j \in I} F(U_i \cap U_j) \mathrel{\substack{\textstyle\leftarrow\\[-0.6ex]
        \textstyle\leftarrow\\[-0.6ex]\textstyle\leftarrow}} \coprod_{i, j, k \in I} F(U_i \cap U_j \cap U_k) \mathrel{\substack{\textstyle\leftarrow\\[-0.6ex]\textstyle\leftarrow\\[-0.6ex]\textstyle\leftarrow\\[-0.6ex]\textstyle\leftarrow}} \cdots  \right),
    \end{equation}
    %
    where the maps are induced by the value of $F$ on the inclusions of opens. There are canonical maps $F(U_i) \rightarrow F(U)$, so that at the level of simplicial objects there is a canonical map
    %
    \begin{equation}
        \cech_{\bullet} (\mathscr{U}_U, F) \xrightarrow{\quad} F(U)_{\bullet},
    \end{equation}
    %
    to the constant simplicial complex at $F(U)$. Since $\catC$ has (sifted) colimits we can take the geometric realization to obtain a morphism
    %
    \begin{equation}
        \cech(\mathscr{U}_U, F) \xrightarrow{\quad} F(U).
    \end{equation}
    %
    $F$ is a (homotopy) cosheaf if, and only if, this morphism is an equivalence for every open set $U$ and every Weiss cover of it $\mathscr{U}_U$.
\end{remark}

All of our definitions above are valid for all topological spaces, so in particular, also stratified spaces. For the next definition of locally constant factorization algebras though, it will be important to specify more information about the space. In other words, they will capture information about the stratification.

@@

\begin{definition}
    The $\infty$-category $\lcfa_M (\catC)$ of \emph{locally constant}\footnote{There is a general definition of locally constant algebra objects in the context of any $\infty$-operad given in \cite[def.2.3.3.20]{lurie_ha}, which, of course, applies here. Our present perspective is more akin to \cite[def.A.1.12]{lurie_ha} whereby we define locally constant cosheaves and then pull this property back to factorization algebras.} \emph{factorization algebras on a stratified manifold $M$ valued in $\catC$} is the full $\infty$-subcategory of $\falg_M (\catC)$ as in the pullback
    %
    \begin{equation}
        \begin{tikzcd}
            \lcfa_M (\catC) \arrow[dr, phantom, "\ulcorner", very near start] \arrow[r] \arrow[d] & \falg_M (\catC) \arrow[d] \\
            \csheaves[W, lc]_M (\catC) \arrow[r] & \csheaves[W]_M (\catC).
        \end{tikzcd}
    \end{equation}
\end{definition}

\begin{remark}\label{rem:sym_mon_inheritance}
    As mentioned in \Cref{rem:inherit_sym_mon_struct}, our assumptions on the target $\catC$ allow the $\infty$-categories of factorization algebras of all varieties to acquire a symmetric monoidal structure from the symmetric monoidal structure of $\catC$ pointwise
    %
    \begin{equation}
        (F \otimes G)(U) = F(U) \otimes G(U).
    \end{equation}
    %
    To satisfy the cosheaf condition we use the property that colimits in $\catC$ commute with its symmetric monoidal structure.

@@

\begin{remark}
    One perspective on this result, provided by \cite[thm.2.43]{aft_fhstrat}, is that the theory of locally constant factorization algebras captures as much information as (generalized) homology theory in the sense of \cite[def.2.37]{aft_fhstrat}.
\end{remark}

@@

% Generate bibliography
\newpage
\printbibliography
